---
title: "East Penn Referee Registrations"
author: "Mike O'Brien"
date: "2/22/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r eprrs-grab}
library(rvest); library(httr); library(dplyr)

# Import roster
eprrs_roster <- read_html('https://usarugby.sportlomo.com/wp-admin/admin-ajax.php?action=getClubMembers&id=11195') %>% 
  html_table(header = T) %>% 
  .[[1]]

eprrs_roster <- eprrs_roster %>% 
  mutate_at(vars(matches('Name')), tolower) %>% 
  group_by(Category) %>% 
  distinct(`First Name`, `Last Name`, .keep_all = T)

# Number of individual registrants
n_regis <- eprrs_roster %>% 
  ungroup() %>% 
  distinct(`First Name`, `Last Name`) %>% 
  nrow()

# Number by category
n_regis_cat <- eprrs_roster %>% 
  tally()

# Those registered as U18
n_regis_u18 <- eprrs_roster %>% 
  filter(Category == 'U18 Referee') %>% 
  select(`First Name`, `Last Name`, Category)

eprrs_output <- eprrs_roster %>% 
  select(`First Name`, `Last Name`, Category) %>% 
  arrange(Category, `Last Name`)
```

```{r epru-clubs}
# Get list of clubs in the CRU
epru <- POST(
  'https://usarugby.sportlomo.com/wp-admin/admin-ajax.php?action=clubMapData',
  body = list(
    id = 6876,
    fetchValues = 'Clubs',
    defaultLabel = 'Club+Name',
    confernce = 'Eastern+Pennsylvania+Rugby',
    typeId = 6853
  ),
  encode = 'form'
)

epru <- epru %>% 
  content(options = 'HUGE') %>% 
  html_element('body') %>% 
  html_element('p')  %>% 
  html_elements('option')

name <- epru %>% html_text(trim = T)
name <- gsub('club_contents.*|[ \t]{2}|[\\"\\,]|\\\\n', '', name)

values <- epru %>% html_attr('value')
values <- gsub('[\\"\\\\]', '', values)


epru <- tibble(name = name, value = values)[-1, ]
```
```{r epru-membership-scrape}
# Pull registrations for RSV-area clubs
epru_registrations <- lapply(
  epru$value,
  function(x){
    tryCatch({
      url <- paste0(
        'https://usarugby.sportlomo.com/wp-admin/admin-ajax.php?action=getClubMembers&id=',
        x
      )
      
      read_html(url) %>% 
        html_table(header = T) %>% 
        .[[1]]
    },
    error = function(e) e
    )
  })
```
```{r epru-membership-clean}
errs <- sapply(epru_registrations, function(x) any(class(x) == 'error'))

epru_registrations <- epru_registrations[!errs]

errs <- sapply(epru_registrations, function(x) nrow(x) == 0)

epru_registrations <- epru_registrations[!errs]

epru_registrations <- bind_rows(epru_registrations)
```
```{r epru-referees}
club_referees <- epru_registrations %>% 
  filter(grepl('Referee', Category)) %>% 
  mutate_at(vars(matches('Name')), tolower) %>% 
  group_by(Category) %>% 
  distinct(`First Name`, `Last Name`, .keep_all = T)


club_referees <- anti_join(club_referees,
                           eprrs_roster,
                           by = c('First Name', 'Last Name')) %>% 
  ungroup() %>% 
  select_at(vars(matches('Name'), Club)) %>% 
  arrange(`Last Name`)
```

This report was automatically created at `r Sys.time()` using the currently-available USA Rugby (USAR) public roster on Sportlomo. Any person who is registered as a referee with a U19 team/club and *NOT* dual-registered with the Eastern Pennsylvania Rugby Referee Society (EPRRS) is not counted below.

  - EPRRS currently has `r n_regis` people registered with USAR.
  - There are `r filter(n_regis_cat, Category == 'Referee 21-22')$n` people registered in the general category, and `r filter(n_regis_cat, Category == 'U18 Referee')$n` registered in the U18 category.
  - There are `r nrow(club_referees)` people registered as a referee with their club, but not EPRRS.

## Referees registered with EPRRS
```{r}
knitr::kable(eprrs_output, format = "simple")
```

## Referees registered with their club, but not EPRRS
### Eastern Pennsylvania Rugby Union
```{r}
knitr::kable(club_referees, format = "simple")
```
