---
title: "Potomac USA Rugby Registrations"
author: "Mike O'Brien"
date: "2/22/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r prr-grab}
library(rvest); library(httr); library(dplyr)

# Import roster
prr_roster <- read_html('https://usarugby.sportlomo.com/wp-admin/admin-ajax.php?action=getClubMembers&id=11193') %>% 
  html_table(header = T) %>% 
  .[[1]]

prr_roster <- prr_roster %>% 
  mutate_at(vars(matches('Name')), tolower) %>% 
  group_by(Category) %>% 
  distinct(`First Name`, `Last Name`, .keep_all = T)

# Number of individual registrants
n_regis <- prr_roster %>% 
  ungroup() %>% 
  distinct(`First Name`, `Last Name`) %>% 
  nrow()

# Number by category
n_regis_cat <- prr_roster %>% 
  tally()

# Those registered as U18
n_regis_u18 <- prr_roster %>% 
  filter(Category == 'U18 Referee') %>% 
  select(`First Name`, `Last Name`, Category)

prr_output <- prr_roster %>% 
  select(`First Name`, `Last Name`, Category) %>% 
  arrange(Category, `Last Name`)
```

```{r cru-clubs}
# Get list of clubs in the CRU
cru <- POST(
  'https://usarugby.sportlomo.com/wp-admin/admin-ajax.php?action=clubMapData',
  body = list(
    id = 6468,
    fetchValues = 'Clubs',
    defaultLabel = 'Club+Name',
    confernce = 'Capital+Rugby+Union',
    typeId = 6853
  ),
  encode = 'form'
)

cru <- cru %>% 
  content(options = 'HUGE') %>% 
  html_element('body') %>% 
  html_element('p')  %>% 
  html_elements('option')

name <- cru %>% html_text(trim = T)
name <- gsub('club_contents.*|[ \t]{2}|[\\"\\,]|\\\\n', '', name)

values <- cru %>% html_attr('value')
values <- gsub('[\\"\\\\]', '', values)


cru <- tibble(name = name, value = values)[-1, ]


cru <- cbind(cru, tibble(prr = c(T, T, T, T, T,
                                 F, F, F, 
                                 T, T, T,
                                 F, 
                                 T, T, T, T, T,
                                 F,
                                 T, 
                                 F, F,
                                 T, T, T,
                                 F, F, F, F,
                                 T, T, T, T, T,
                                 F,
                                 T, T,
                                 F, F, F, F, F, F, F,
                                 T, T, T, T,
                                 F, F,
                                 T, T, T, T, T, T, T, T, T)))
```
```{r cru-membership-scrape}
# Pull registrations for PRR-area clubs
cru_registrations <- lapply(
  cru[cru$prr == T,]$value,
  function(x){
    tryCatch({
      url <- paste0(
        'https://usarugby.sportlomo.com/wp-admin/admin-ajax.php?action=getClubMembers&id=',
        x
      )
      
      read_html(url) %>% 
        html_table(header = T) %>% 
        .[[1]]
    },
    error = function(e) e
    )
  })
```
```{r cru-membership-clean}
errs <- sapply(cru_registrations, function(x) any(class(x) == 'error'))

cru_registrations <- cru_registrations[!errs]

errs <- sapply(cru_registrations, function(x) nrow(x) == 0)

cru_registrations <- cru_registrations[!errs]

cru_registrations <- bind_rows(cru_registrations)
```
```{r cru-referees}
club_referees <- cru_registrations %>% 
  filter(grepl('Referee', Category)) %>% 
  mutate_at(vars(matches('Name')), tolower) %>% 
  group_by(Category) %>% 
  distinct(`First Name`, `Last Name`, .keep_all = T)


club_referees <- anti_join(club_referees,
                           prr_roster,
                           by = c('First Name', 'Last Name')) %>% 
  ungroup() %>% 
  select_at(vars(matches('Name'), Club)) %>% 
  arrange(`Last Name`)
```

This report was automatically created at `r Sys.time()` using the currently-available USA Rugby (USAR) public roster on Sportlomo. Any person who is registered as a referee with a U19 team/club and *NOT* dual-registered with the Potomac Society of Rugby Football Referees (PSFRF; PRR) is not counted below.

  - PRR currently has `r n_regis` people registered with USAR.
  - There are `r filter(n_regis_cat, Category == 'Referee 21-22')$n` people registered in the general category, and `r filter(n_regis_cat, Category == 'U18 Referee')$n` registered in the U18 category.
  - There are `r nrow(club_referees)` people registered as a referee with their club, but not PRR.

## Referees registered with PRR
```{r}
knitr::kable(prr_output, format = "simple")
```

## Referees registered with their club, but not PRR
### Capital Rugby Union
```{r}
knitr::kable(club_referees, format = "simple")
```

